Paper Analysis

### 2025-04-29 Paper_WriteUp/Paper_Plots.qmd
updating glicko2() calculation to use RD and volatility from previous game. Not constant anymore

#storage
glicko_sim = matrix(NA, nrow = num_games, ncol = num_sims)
game_sim = matrix(NA, nrow = num_games, ncol = num_sims)
#probs = matrix(NA, nrow = num_games, ncol = num_sims) #for debugging

@@

  ## if first game use default history (0), otherwise use the previous
  if (i == 1) {
    curr_rating = curr_game_info$focal_rating
    curr_hist = 0.5 #assume they're current past performance is at their usual level
  } else {
    curr_hist = curr_game_info$hist
    curr_rating = glicko_sim[i - 1, j]
  }

@@

  #find rating
  games = data.frame(Week = i,
                     Player1 = users[focal_player_used],
                     Player2 = opp,
                     Score = sim_result)
  initstate = tibble(Player = c(users[focal_player_used], opp),
                     Rating = c(curr_rating, opp_rating),
                     Deviation = 50,
                     Volatility = 0.04)

@@

  #store current result and rating
  glicko_sim[i, j] = as.numeric(focal_glick)[1]
  game_sim[i, j] = sim_result
  }
  if(i %% 10 == 0) {print(i)} #progress of number of games simulated
}

>>>>

#storage
glicko_sim = matrix(NA, nrow = num_games, ncol = num_sims) #storing the ratings
rd_sim = matrix(NA, nrow = num_games, ncol = num_sims) #storing the RDs
volatility_sim = matrix(NA, nrow = num_games, ncol = num_sims) #storing the volatilities
game_sim = matrix(NA, nrow = num_games, ncol = num_sims) #storing the game results
#probs = matrix(NA, nrow = num_games, ncol = num_sims) #for debugging

### SET FIRST RD, VOLATILITY TO TRUE RD/VOLATILITY WE GET AFTER FINDING RDS/VOLATILITY IN RAW DATASET (IN INIT CALCULATION)

@@

  ## if first game use default history (0), otherwise use the previous
  if (i == 1) {
    curr_rating = curr_game_info$focal_rating
    curr_rd = 50 #starting value for rating deviation
    curr_volatility = 0.04 #starting value for volatility
    curr_hist = 0 #assume they're current past performance is NULL
  } else {
    #use rating info from past game
    curr_rating = glicko_sim[i - 1, j]
    curr_rd = rd_sim[i - 1, j]
    curr_volatility = volatility_sim[i - 1, j]
    curr_hist = curr_game_info$hist
  }

@@

  #find rating
  games = data.frame(Week = i,
                     Player1 = users[focal_player_used],
                     Player2 = opp,
                     Score = sim_result)
  initstate = tibble(Player = c(users[focal_player_used], opp),
                     Rating = c(curr_rating, opp_rating),
                     Deviation = curr_rd,
                     Volatility = curr_volatility)

@@

  #store current result and rating info
  glicko_sim[i, j] = as.numeric(focal_glick)[1]
  rd_sim[i, j] = as.numeric(focal_glick)[2]
  volatility_sim[i, j] = as.numeric(focal_glick)[3]
  game_sim[i, j] = sim_result
  }
  if(i %% 10 == 0) {print(i)} #progress of number of games simulated
}
